Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
editing IV-B, finished Step 2

$T(p_j)$ is the set of tasks already scheduled on $p_j$; by step 1, their files are
already in the memory of~$p_j$. However, the files from the
other predecessor tasks must be loaded in memory before executing task~$v$,
as well as $m_v$ and the data generated for all successor tasks.
$Res$ is then checking whether there was enough memory; if it is negative,
it means that we have exceeded the memory of~$p_j$ with this tentative
assignment.

In this case ($Res <0$), we try evicting
some data from memory so that we have enough memory to execute task~$v$.
We need to evict at least $Res$ data.
We propose a greedy approach, evicting the largest files of $\PD_j$ until $Res$ data has been evicted. 
A variant where the smallest files are evicted first has been tested, and it led to comparable results. 
%    
%    in order to avoid costly communications.
%    \AB{FYI We initially discussed evicting the largest files, but this leads to
%    large communications and does not seem efficient after all... Maybe we can think of another
%    approach that would take into account both data size and bottom level...}
While tentatively evicting files, we remove them from the list of pending memories and move them into a list
of memories pending in the communication buffer.
We keep track of the available buffer size, too -- each time a file gets moved into the pending in buffer, 
the available buffer size is reduced by its weight.

If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
or if while doing so we exceeded the size of the available buffer,
we set the finish time to~$+\infty$ (invalid choice).

>>>>

$T(p_j)$ is the set of tasks already scheduled on $p_j$; by Step 1, their files are
already in the memory of~$p_j$. However, the files from the
other predecessor tasks must be loaded into memory before executing task~$v$,
as well as the task data of size $m_v$, and the data generated for all successor tasks.
$Res$ then checks whether there is enough memory; if it is negative,
we have exceeded the memory of~$p_j$ with this tentative assignment.
%
In this case ($Res <0$), we try to evict some data from memory so that there is enough memory to execute task~$v$.
Clearly, we need to evict at least $Res$ data.
To this end, we propose a greedy approach, which evicts the largest files of $\PD_j$ until data of size $Res$ have been evicted. 
A variant where the smallest files are evicted first has been tested; it led to comparable results. 
%    
%    in order to avoid costly communications.
%    \AB{FYI We initially discussed evicting the largest files, but this leads to
%    large communications and does not seem efficient after all... Maybe we can think of another
%    approach that would take into account both data size and bottom level...}
While tentatively evicting files, we remove them from the list of pending memories and move them into a list
of memories pending in the communication buffer.
We keep track of the available buffer size, too -- every time a file is moved into the pending buffer, 
the available buffer size is reduced by the file size.

If, after tentatively evicting all files from $\PD_j$, we still do not have enough memory, or if we exceed the size of the available buffer during this process, we set the finish time to $+\infty$ (indicating an invalid choice).
